Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-16 surfaces-write-up/surface-write-up.tex
minor intro edit

The work in this paper also has relations to certain rings of Hilbert 
modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
modular forms are both to higher dimensions variables. In the case of 
Hilbert Modular forms, one considers modular forms on an $m$ fold product 
of upper half planes, which transform under the action of finite index 
subgroups of the groups of positive determinant matrices. Similarly, Siegel 
modular forms are modular forms on the Siegel upper half space which are 
stable under the action of the symplectic group.

>>>>

The work in this paper also has relations to certain rings of Hilbert 
modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
modular forms are both to higher dimensions variables. In the case of 
Hilbert Modular forms, one considers modular forms on a product of $m$
upper half planes, which transform under the action of finite index 
subgroups of the groups of positive determinant matrices. Similarly, Siegel 
modular forms are modular forms on the Siegel upper half space which are 
stable under the action of the symplectic group.
